Do larger catchments respond different to forest cover change? Re-analysing a global data set.

### 2021-11-25 paper/Forest_and_Water/Forest_and_Water.tex
Update Forest_and_Water.tex

  \title{Do larger catchments respond different to forest cover change?
Re-analysing a global data set.}
    \author[The University of Sydney, INIA]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi\corref{2}}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{INIA, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Departamento
de Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{../../data/FAOET0data} \caption{Distribution of included catchments across the globe based on reported or estimated latitude and longitude}\label{fig:global_map}
\end{figure}

>>>>

  \title{Do larger catchments respond different to forest cover change?
Re-analysing a global data set.}
    \author[The University of Sydney, INIA]{R. Willem Vervoort\corref{1}}
   \ead{willem.vervoort@sydney.edu.au} 
    \author[INIA]{Eliana Nervi\corref{2}}
   \ead{eliananervi@gmail.com} 
    \author[IMFIA]{Jimena Alonso\corref{2}}
   \ead{jalonso@fing.edu.uy} 
      \address[The University of Sydney]{School of Life and Environmental Sciences, The University of Sydney,
Sydney, NSW 2006, Australia}
    \address[INIA]{Instituto Nacional de Investigación Agropecuaria, INIA-Uruguay, Ruta 48
km 10, Rincon del Colorado, 90100 Canelones, Uruguay}
    \address[IMFIA]{Institute of Fluid Mechanics and Environmental Engineering, School of
Engineering, Universidad de la República, 11200 Montevideo, Uruguay}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

\begin{figure}
\includegraphics[width=0.9\linewidth]{../../data/FAOET0data2} \caption{Distribution of included catchments across the globe based on reported or estimated latitude and longitude}\label{fig:global_map}
\end{figure}
